GMSE: an R package for generalised management strategy evaluation

### 2017-08-07 notebook/ms/ms.Rmd
Add generation indicator to Figure 1

```{r, echo = FALSE, fig.height = 4, fig.width = 4, fig.align = 'left', fig.cap = "Description of the generalised management strategy evaluation framework"}
mbox <- function(x0, x1, y0, y1){
    xx <- seq(from=x0, to=x1, length.out = 100);
    yy <- seq(from=y0, to=y1, length.out = 100);
    xd <- c(rep(x0, 100), xx, rep(x1,100), rev(xx));
    yd <- c(yy, rep(y1,100), rev(yy), rep(y0, 100));
    return(list(x=xd, y=yd));
}
par(mar=c(0,0,0,0));
plot(x = 0, y = 0, type = "n", xlim = c(0, 100), ylim = c(0, 100), 
     xaxt = "n", yaxt = "n", xlab = "", ylab = "");
# Manager model 
manger_model_box <- mbox(x0 = 1, x1 = 30, y0 = 70, y1 = 99);
polygon(x = manger_model_box$x, y = manger_model_box$y, lwd = 3);
text(x = 15, y = 90, cex = 1.0, labels = "Manager");
text(x = 15, y = 83, cex = 1.0, labels = "model");
# User model
user_model_box <- mbox(x0 = 70, x1 = 99, y0 = 70, y1 = 99);
polygon(x = user_model_box$x, y = user_model_box$y, lwd = 3);
text(x = 85, y = 90, cex = 1.0, labels = "User");
text(x = 85, y = 83, cex = 1.0, labels = "model");
# Observation model
observe_model_box <- mbox(x0 = 1, x1 = 30, y0 = 1, y1 = 30);
polygon(x = observe_model_box$x, y = observe_model_box$y, lwd = 3);
text(x = 15, y = 23, cex = 1.0, labels = "Observation");
text(x = 15, y = 15, cex = 1.0, labels = "model");
# Resource model
resource_model_box <- mbox(x0 = 70, x1 = 99, y0 = 1, y1 = 30);
polygon(x = resource_model_box$x, y = resource_model_box$y, lwd = 3);
text(x = 85, y = 23, cex = 1.0, labels = "Natural");
text(x = 85, y = 15, cex = 1.0, labels = "resources");
text(x = 85, y = 7,  cex = 1.0, labels = "model");
# Game-theoretic (genetic algorithm) model
game_model_box <- mbox(x0 = 36, x1 = 65, y0 = 36, y1 = 65);
polygon(x = game_model_box$x, y = game_model_box$y, lwd = 3);
text(x=50, y=55, labels="Genetic", cex=1.0);
text(x=50, y=48, labels="algorithm", cex=1.0);
# Arrows indicating direction of GMSE model
arrows(x0=15, x1=15, y0=30, y1=70, lwd=2, length=0.15);
arrows(x0=30, x1=70, y0=85, y1=85, lwd=2, length=0.15);
arrows(x0=85, x1=85, y0=70, y1=30, lwd=2, length=0.15);
arrows(x0=70, x1=30, y0=15, y1=15, lwd=2, length=0.15);
arrows(x0=30, x1=36, y0=70, y1=65, lwd=2, length=0.075, code=3);
arrows(x0=65, x1=70, y0=65, y1=70, lwd=2, length=0.075, code=3);
text(x=50, y=90, labels="Policy", cex = 1.0);
text(x=50, y=20, labels="Monitoring", cex = 1.0);
text(x=10, y=48, labels="Indicators", srt=90, cex = 1.0);
text(x=90, y=52, labels="Off-take", srt=-90, cex = 1.0);
```

>>>>

```{r, echo = FALSE, fig.height = 4, fig.width = 4, fig.align = 'left', fig.cap = "Description of one time step of the generalised management strategy evaluation framework"}
mbox <- function(x0, x1, y0, y1){
    xx <- seq(from=x0, to=x1, length.out = 100);
    yy <- seq(from=y0, to=y1, length.out = 100);
    xd <- c(rep(x0, 100), xx, rep(x1,100), rev(xx));
    yd <- c(yy, rep(y1,100), rev(yy), rep(y0, 100));
    return(list(x=xd, y=yd));
}
par(mar=c(0,0,0,0));
plot(x = 0, y = 0, type = "n", xlim = c(0, 100), ylim = c(0, 100), 
     xaxt = "n", yaxt = "n", xlab = "", ylab = "");
# Manager model 
manger_model_box <- mbox(x0 = 1, x1 = 30, y0 = 70, y1 = 99);
polygon(x = manger_model_box$x, y = manger_model_box$y, lwd = 3);
text(x = 15, y = 90, cex = 1.0, labels = "Manager");
text(x = 15, y = 83, cex = 1.0, labels = "model");
# User model
user_model_box <- mbox(x0 = 70, x1 = 99, y0 = 70, y1 = 99);
polygon(x = user_model_box$x, y = user_model_box$y, lwd = 3);
text(x = 85, y = 90, cex = 1.0, labels = "User");
text(x = 85, y = 83, cex = 1.0, labels = "model");
# Observation model
observe_model_box <- mbox(x0 = 1, x1 = 30, y0 = 1, y1 = 30);
polygon(x = observe_model_box$x, y = observe_model_box$y, lwd = 3);
text(x = 15, y = 23, cex = 1.0, labels = "Observation");
text(x = 15, y = 15, cex = 1.0, labels = "model");
# Resource model
resource_model_box <- mbox(x0 = 70, x1 = 99, y0 = 1, y1 = 30);
polygon(x = resource_model_box$x, y = resource_model_box$y, lwd = 3);
text(x = 85, y = 23, cex = 1.0, labels = "Natural");
text(x = 85, y = 15, cex = 1.0, labels = "resources");
text(x = 85, y = 7,  cex = 1.0, labels = "model");
# Game-theoretic (genetic algorithm) model
game_model_box <- mbox(x0 = 36, x1 = 65, y0 = 36, y1 = 65);
polygon(x = game_model_box$x, y = game_model_box$y, lwd = 3);
text(x=50, y=58, labels="Genetic", cex=1.0);
text(x=50, y=51, labels="algorithm", cex=1.0);
sc1 <- seq(from = 0, to = pi, by = 0.001);
sc2 <- seq(from = pi, to = 2*pi, by = 0.001);
points(x = 2*cos(sc1) + 41, y = 42 + 2*sin(sc1), lwd = 1.5, type = "l");
points(x = 2*cos(sc2) + 41, y = 40 + 2*sin(sc2), lwd = 1.5, type = "l");
arrows(x0 = 43, x1 = 43, y0 = 42, y1 = 41, lwd = 1.5, length = 0.06);
arrows(x0 = 39, x1 = 39, y0 = 40, y1 = 41, lwd = 1.5, length = 0.06);
text(x=43, y=42, labels="Multiple", cex=0.7, pos = 4);
text(x=43, y=39, labels="Generations", cex=0.7, pos = 4);
# Arrows indicating direction of GMSE model
arrows(x0=15, x1=15, y0=30, y1=70, lwd=2, length=0.15);
arrows(x0=30, x1=70, y0=85, y1=85, lwd=2, length=0.15);
arrows(x0=85, x1=85, y0=70, y1=30, lwd=2, length=0.15);
arrows(x0=70, x1=30, y0=15, y1=15, lwd=2, length=0.15);
arrows(x0=30, x1=36, y0=70, y1=65, lwd=2, length=0.075, code=3);
arrows(x0=65, x1=70, y0=65, y1=70, lwd=2, length=0.075, code=3);
text(x=50, y=90, labels="Policy", cex = 1.0);
text(x=50, y=20, labels="Monitoring", cex = 1.0);
text(x=10, y=48, labels="Indicators", srt=90, cex = 1.0);
text(x=90, y=52, labels="Off-take", srt=-90, cex = 1.0);
```
